Simulating High-Dimensional Multivariate Data

### 2020-12-01 050-examples.Rmd
reduce size of large figures

```{r ch050-simDataFig, echo = FALSE, eval=T, cache=F, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap='Simulated data for 3 selected high-expressing genes, replicating the observed data structure.'}
exampleGenes <- readRDS(file = './data/exampleGenes.rds')
GGally::ggpairs(
  data = as.data.frame( sim_nbinom[ ,exampleGenes] ), 
  upper = list(
    continuous = GGally::wrap('cor', method = "spearman")
  ), 
) + theme_bw()
```

@@

```{r ch050-figBRCA, echo=F, eval=T, cache=F, fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
## estimate rho from sims and plot
nb_Rho_hat <- cor_fast(sim_nbinom, method = corType)
## triplot
par(mfrow=c(1,3))
plot(nb_Rho[lower.tri(nb_Rho)], nb_Rho_hat[lower.tri(nb_Rho_hat)],
     xlim = c(-1, 1), ylim = c(-1, 1),
     pch = 1, cex = 1, col = rgb(0, 0, 0, 0.05),
     xlab = "Target Correlation", ylab = "Estimated Correlation",
     main = "Spearman Cor. Matching")
abline(a = 0, b = 1, col="red", lty="dashed")
## estimate prob,size from sims and plot
nbinom_size_prob_hat <- apply(sim_nbinom, 2, nbinom_mom)
plot(sizes, nbinom_size_prob_hat[1,],
     pch = 1, cex = 1, col = rgb(0, 0, 0, 1),
     xlab = "Target Size", ylab = "Estimated Size",
     main = "Marginal NB Size Matching")
abline(a=0, b=1, col="red", lty="dashed")
plot(log(probs), log(nbinom_size_prob_hat[2,]),
     pch = 1, cex = 1, col = rgb(0, 0, 0, 1),
     xlab = "Target Log Probability", ylab = "Estimated Log Probability",
     main = "Marginal NB Prob Matching")
abline(a=0, b=1, col="red", lty="dashed")
par(mfrow=c(1,1))
```

@@

The standard `R` summary function supplies the mean-augmented five-number summary of the quadratic loss distribution computed above.

>>>>

```{r ch050-makeSimDataFig, echo = FALSE, eval=T, cache=F, message=FALSE, warning=FALSE}
if( !file.exists("fig/ch050-simDataFig.png") ) {
    exampleGenes <- readRDS(file = './data/exampleGenes.rds')
    p <- GGally::ggpairs(
                     data = as.data.frame( sim_nbinom[ ,exampleGenes] ), 
                     upper = list(
                         continuous = GGally::wrap('cor', method = "spearman")
                     )) + theme_bw()
    ## ggsave("fig/ch050-simDataFig.png", plot = p, width = 5, height = 4, dpi = 300)
    ggsave("fig/ch050-simDataFig.png", plot = p, dpi = 300) 
}
```

```{r ch050-simDataFig, echo=F, fig.align='center', fig.cap='Simulated data for three selected high-expressing genes replicates the estimated data structure.'}
knitr::include_graphics('fig/ch050-simDataFig.png')
```

@@

```{r ch050-makeFigBRCA, echo=F, eval=T, cache=F}
if( !file.exists("fig/ch050-figBRCA.png") ) {
    ## estimate rho from sims and plot
    nb_Rho_hat <- cor_fast(sim_nbinom, method = corType)
    ## triplot
    ## png("fig/ch050-figBRCA.png", width = 4, res = 100, units = 'in')
    png("fig/ch050-figBRCA.png", res = 300, width = 5, height = 4, units = 'in')
    par(mfrow=c(1,3))
    plot(nb_Rho[lower.tri(nb_Rho)], nb_Rho_hat[lower.tri(nb_Rho_hat)],
         xlim = c(-1, 1), ylim = c(-1, 1),
         pch = 1, cex = 1, col = rgb(0, 0, 0, 0.05),
         xlab = "Target Correlation", ylab = "Estimated Correlation")
         ## main = "Spearman Cor. Matching")
    abline(a = 0, b = 1, col="red", lty="dashed")
    ## estimate prob,size from sims and plot
    nbinom_size_prob_hat <- apply(sim_nbinom, 2, nbinom_mom)
    plot(sizes, nbinom_size_prob_hat[1,],
         pch = 1, cex = 1, col = rgb(0, 0, 0, 1),
         xlab = "Target Size", ylab = "Estimated Size")
         ## main = "Marginal NB Size Matching")
    abline(a=0, b=1, col="red", lty="dashed")
    plot(log(probs), log(nbinom_size_prob_hat[2,]),
         pch = 1, cex = 1, col = rgb(0, 0, 0, 1),
         xlab = "Target Log Probability", ylab = "Estimated Log Probability")
         ## main = "Marginal NB Prob Matching")
    abline(a=0, b=1, col="red", lty="dashed")
    dev.off()
    par(mfrow=c(1,1))
}
```

```{r ch050-figBRCA, echo=F, out.width = '80%', fig.align='center', fig.cap="Simulated random vectors from a multivariate negative binomial replicate the estimated structure from an RNA-seq data set. The dashed red lines indicated equality between estimated parameters from simulated data (vertical axes) and the specified target parameters (horizontal axes)."}
knitr::include_graphics('fig/ch050-figBRCA.png')
```

@@

The `R` summary function supplies the mean-augmented five-number summary of the quadratic loss distribution computed above.
